Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-20 papers/histogram/sad.tex
added in the citations for global minimum.
edit paper to remove smaller bin size

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv}
  \caption{The heat capacity of the LJ31 cluster after $10^{12}$ moves
    as calculated with each method.  Each simulation used a bin size
    of $\Delta E=0.01\epsilon$.  The dotted black line labeled
    ``converged result'' was a $1/t$-WL simulation with the energy
    constrained to a range $-133.53\epsilon\le E\le -110\epsilon$,
    all other simulations had a maximum allowed energy of zero.  The
    ``converged result'' therefore is only converged at low temperatures.}
  \label{fig:lj-cv}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv-error}
  \caption{The maximum error in the heat capacity of the LJ31 cluster
    in the temperature range 0.01~$\epsilon\le k_BT \le 0.05\epsilon$.
    Note that the value of $C_V$ ranges from 90$k_B$ to 120$k_B$, so
    the smallest (maximum) errors seen are around 1\%.  All WL methods
    shown were run with a histogram bin width of $\Delta
    E=0.01\epsilon$.  Their convergence at other bin widths was
    similar to that of SAD. }
  \label{fig:lj-cv-error}
\end{figure}

@@

Figure~\ref{fig:lj-cv-error} shows the largest error in heat capacity
at low temperatures as a function of the number of Monte Carlo moves
performed.
%
We explored the convergence behavior of each algorithm as a function
of bin width, but show only the results for SAD.  Both the WL and
$1/t$-WL algorithms showed similar behavior to SAD.  In each of these
algorithms, the rate of convergence of the heat capacity is roughly
independent of the bin width.  In contrast (but not shown) the entropy
itself shows significantly larger statistical errors with smaller bin
sizes.  The canonical averaging process in Eq.~\ref{eq:cv} averages
out those statistical fluctuations, largely eliminating the penalty of
using a smaller bin size.

@@

We found the convergence of the WL and $1/t$-WL to be incredibly
sensitve to the minimum energy chosen, complicating the process of
obtaining a workable result.  The known ground state energy of this
cluster is \davidsays{look up and cite}.  With a minimum energy of
$-133.58\epsilon$, our simulation did not converge in 10$^{12}$ moves.
With minimum energies of $-133.54\epsilon$, $-133.53\epsilon$, and
$-133.52\epsilon$, the simulations do seem to converge, although the
lowest energy case was significantly slower and never reached as small
an error.  This result highlights the advantage of being able to
specify a temperature range rather than an energy range when computing
properties as a function of temperature.  It is not only more
convenient, but also far more efficient due the the fact that only a
single simulation need be performed.

@@

\jpcom{mention something about LJ clusters and what we find!}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv}
  \caption{The heat capacity of the LJ31 cluster after $10^{12}$ moves
    as calculated with each method.  Each simulation used a bin size
    of $\Delta E=0.01\epsilon$.}
  \label{fig:lj-cv}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/lj-cv-error}
  \caption{The maximum error in the heat capacity of the LJ31 cluster
    in the temperature range 0.01~$\epsilon\le k_BT \le 0.05\epsilon$.
    Note that the value of $C_V$ ranges from 90$k_B$ to 120$k_B$, so
    the smallest (maximum) errors seen are around 1\%.  All WL methods
    shown were run with a histogram bin width of $\Delta
    E=0.01\epsilon$.  The converged reference heat capacity was
    computed with a $1/t$-WL simulation with the energy constrained to
    a range $-133.53\epsilon\le E\le -110\epsilon$.
  }
  \label{fig:lj-cv-error}
\end{figure}

@@

Figure~\ref{fig:lj-cv-error} shows the maximum error in heat capacity
in the temperature range $0.01\epsilon\le k_BT\le 0.05\epsilon$ as a
function of the number of Monte Carlo moves performed.
%
We explored the convergence behavior of each algorithm at two energy
bin widths ($\Delta E=0.01\epsilon$ and $\Delta E=0.1\epsilon$).  We
were unable to converge the WL or $1/t$-WL algorithms with the larger
bin size.
%
The rate of convergence for the heat capacity seems to be roughly
independent of the bin width.  In contrast (but not shown) the entropy
itself shows much larger statistical fluctuations with smaller bin
sizes.  The canonical averaging process in Eq.~\ref{eq:cv} averages
out those statistical fluctuations, which reduces the penalty of using
a smaller bin size.

@@

We found the convergence of the WL and $1/t$-WL to be incredibly
sensitive to the minimum energy chosen, complicating the process of
obtaining a workable result.  The known ground state energy of this
cluster is $-133.586422\epsilon$~\cite{northby1987structure,
  wales1997global}.  With a minimum energy of $-133.58\epsilon$, none
of our simulations converged in 10$^{12}$ moves.  With minimum
energies of $-133.54\epsilon$, $-133.53\epsilon$, and
$-133.52\epsilon$, the simulations do seem to converge, although the
lowest energy case was significantly slower and never reached as small
an error.  This result highlights the advantage of being able to
specify a temperature range rather than an energy range when computing
properties as a function of temperature.  It is not only more
convenient, but also far more efficient due the the fact that only a
single simulation need be performed.

@@

We found that for examining low-energy structures of a Lennard-Jones
cluster the WL and $1/t$-WL algorithms---versions of which had
previously found to be unsuccessful on this problem~\cite{}---have
convergence properties that are highly dependent on the choice of
energy range to be examined.  This is particularly problematic when
examining the low-temperature heat capacity, where it is difficult to
determine the lowest energy that will have a significant impact at the
temperatures of interest.
